% Explain who you are, what your role is and why this project is relevant to yourself, remember the assessor will not have met you before.
% Give some context with relevant information on the organisation.

\section{Introduction and background}

I am a Software Engineer at the BBC, Team Lead for the Sounds web team, and I have been training as a Data Scientist,
working in attachment with the iPlayer Recommendation team.

I built a machine learning model pipeline that generates content-to-content (C2C) similarity recommendations
of video on-demand (VOD), for the ``More Like This'' section on BBC iPlayer \cite{BBC:MoreLikeBluey}.
This project is relevant to me because I have been crossing paths with the world of recommendations
multiple times during my career at the BBC, and it sparked an interest in it.
I had a tangent encounter back in 2015 while working for a team that was building
an initial recommender for BBC News, and an API to provide recommendations using 3rd party engines.
I also produced and presented a talk for a Hack Day. The talk was called ``Recommendation Assumptions'' \cite{RecsAssumptions},
and it was about types of recommendations, and contextual external factors affecting
them. Until now, when I was able to finally put my knowledge into practice
with an actual project on real data.

The BBC is a well-known British broadcaster, and it is always evolving to remain relevant to its audience. Its mission
is to inform, educate and entertain, and it operates within the boundaries set by the Royal Charter \cite{BBC:RoyalCharter}.
The current media landscape requires the BBC to deliver digital-first content that is relevant to the audience,
and this involves investments in data and personalised services, not to mention a certain revolution in
generative machine learning modelling that is keeping everyone busy.
