% Provide high-level overview of the methods (e.g. regression) and tools used
% with justification explaining why these methods are suitable for the problem at hand.
% Justification may include factors such as the need for interpretability, transparency
% or the timescales you had to work with.

\section{Methods and justification}

\subsection{Data pre-processing}

I used \textbf{one-hot encoding} to transform the categorical features (i.e. the metadata annotations) into a numerical vector.
It is a simple yet effective encoding method and is perfect for transforming nominal categoricals because it doesn’t introduce
any ranking or arithmetic relationship among the encoded values.
The downside of this approach is that it generates high-dimensional sparse arrays,
introducing the so-called \textit{curse of dimensionality} problem.
Nonetheless, this curse became a blessing for the adopted modelling technique,
which needed high-dimensional data to produce quality results.

\subsection{Modelling and regularisation}

I trained an \textbf{autoencoder} \cite{DBLP:journals/corr/abs-2003-05991,DBLP:journals/corr/abs-2201-03898}
to learn the Passport tags' latent features and reduce the encoded vectors' size.
The autoencoder is an encoder-decoder neural network, a self-supervised model capable of capturing non-linearity from the data.
I used the ``undercomplete'' variant, which constrains the number of nodes in the hidden layers, creating a ``bottleneck''
of information flow through the network.
This bottleneck is a form of \textit{regularisation} that forces the model to learn latent attributes from the input
while reconstructing it with minimal loss. Ultimately, it helps prevent the model from overfitting the training dataset by indexing it like a caching layer.

I extracted the trained \textit{encoder} segment of the network to compress the one-hot encoded high-dimensional sparse array into
a lower-dimensional and denser representation called \textit{embedding} \cite{GoogleForDevelopers:Embeddings}.
This technique solved the curse of dimensionality and the data sparsity problems and improved the calculation
complexity and the quality of the recommendations at inference time.

To improve and assess the ability of the model to \textit{generalise} on unseen data, I randomly shuffled the dataset and split
it into three chunks: training, validation and test. I used \textbf{hyperparameter tuning} to find the best model parameters
that minimised the cost function and used the validation set to regularise the model with \textbf{early stopping}.
This technique monitored the reconstruction loss on an out-of-sample dataset,
allowing the model to stop training within a set ``patience'' threshold after reaching a local minimum on the validation error.
The test set was finally used to assess the model's performance using the best set of parameters.

I used \textbf{dropout} to further regularise the model and make it robust to small changes in the input,
and \textbf{data augmentation}, by including in the training data the episodes that shared the same tags with their
parent programme. \textbf{Weight decay} and \textbf{batch normalisation} were tested during hyperparameter tuning and discarded for poor performance.

\subsection{Content similarity}

Content similarity was calculated with the \textbf{cosine} of the angle $\theta$ between each pair of embeddings \cite{GoogleForDevelopers:EmbeddingSimilarity}.
This metric is insensitive to the magnitude of the vectors. Because high-frequency values tend to have a larger magnitude,
it mitigates the impact of popularity in the similarity calculation.
One-hot encoded vectors lack meaningful relations between them.
They represent unit vectors bound in the ``positive quadrant'' of a Cartesian coordinate system for a multidimensional Euclidean space.
Because each pair can only have a finite number of angles,
the cosine similarity will also assume a finite number of discrete values between 0 and 1, causing information
loss. Ideally, we would expect the similarity score to assume a continuous value bound between -1 and 1, and this
is only possible if the angle $\theta$ of any vector pair can assume a value between 0 and 360 (i.e. $0\pi$ and $2\pi$), hence
the use of embeddings.

\subsection{Tools and frameworks}

The entire project was written in \textbf{Python}. It is the \textit{de facto} programming language for data science
and machine learning tasks. Python has an established, diverse and well-documented ecosystem of external libraries
and frameworks that facilitated the job, and it is also the language of choice at the BBC.

I used \textbf{Pandas} only for tabular data manipulation to generate and store the one-hot encoded vectors.
Unfortunately, using it for exploratory data analysis (EDA) wasn't possible because the iPlayer catalogue
had roughly one year's worth of data, which didn't fit in memory, causing Pandas to crash.
Therefore, I used \textbf{Dask}, a library capable of running out-of-memory and parallel execution
for faster processing on single-node machines and distributed computing on multi-node machines
while using the familiar Pandas API.

I used \textbf{TensorFlow} and \textbf{Keras} for modelling to build and train the encoder-decoder neural network architecture.
\textbf{Keras Tuner} for hyperparameters tuning.
I also used \textbf{Scikit-learn} but not for modelling. It provided utility functions for the dataset splitting and
the cosine similarity calculation, and I was already familiar with its API.

I used a combination of \textbf{Matplotlib} and \textbf{Seaborn} for visualisation and \textbf{rdflib} to fetch and parse
the RDF documents from the BBC Ontology to extract the labels needed to visualise the recommendations for testing purposes.
Worth also mentioning the use of \textbf{pytest} for unit testing and \textbf{black} for PEP 8 code compliance and formatting.
Finally, I used \textbf{Jupyter Lab} to edit the project, \textbf{git} for code versioning, \textbf{GitHub} as a remote code repository
and for collaboration, and \textbf{AWS Sagemaker} to run the pipeline on more capable virtual machines, especially during hyperparameter tuning.
