% Explain who you are, what your role is and why this project is relevant to yourself, remember the assessor will not have met you before.
% Give some context with relevant information on the organisation.

\section{Introduction and background}

I am a Software Engineer at the BBC, Team Lead for the Sounds web team, and I have been training as a Data Scientist,
working in attachment with the iPlayer Recommendation team.

I built a machine learning model pipeline that produces content-to-content (C2C) similarity recommendations
of video on-demand (VOD), for the "More Like This" section on BBC iPlayer \cite{MoreLikeBluey}.
This project is relevant to me because it is about recommendations, and I have been crossing paths with this world
multiple times during my career at the BBC. This sparked an interest in it.
I had a tangent encounter back in 2015, while working for a team that was building
an initial recommender for BBC News and an API to provide recommendations using 3rd party engines.
During a Hack Day some time later, I produced and presented a talk called
"Recommendation Assumptions" \cite{RecsAssumptions}, which was about type of recommendations and external factors affecting
them, which are contextual to the consumption of the content itself. Until today, where I can finally put my knowledge into practice
with an actual project on real data.

The BBC is a well-known British broadcaster, and it is always evolving to remain relevant to its audience. Its mission
is to inform, educate and entertain, and it operates within the boundaries set by the Royal Charter \cite{RoyalCharterBBC}.
The current media landscape requires the BBC to deliver digital-first content that is relevant to the audience,
and this involves investements in data and personalised services, not to mention a certain revolution in machine learning
that is keeping everyone busy.
